Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-28 draft/ms_v5.tex
Other performances

@@

    The \s2n{} for PSF photometry is defined as
    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band. 
    Figure \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} 
    in the $g$- and $i$-bands. 
    This Figure shows the expected \s2n{} of stars as a function of magnitude in the 
    Wide layer.
    The slopes and scatters of these relations are very similar to the ones using 
    real stars on these two \tracts{}.

    Figure \ref{fig:star_sn} show that seeing conditions impact the \s2n{} of point
    sources at fixed input magnitude.
    In $i$-band, the bad-seeing (0.7\asec{}) \tract{} shows systematically
    lower \s2n{} than the good-seeing (0.5\asec{}) \tract{}.
    The \s2n{} is similar for the two $g$-band \tracts{} because they share similar 
    seeing conditions.

@@

    Figure \ref{fig:psf_mag} also shows that the precision of the PSF photometry is 
    not filter dependent. 
    The precision of \forced{} PSF magnitudes in $r$ and $z$ is similar to the results
    for $i$-band. 
    For $r$ band we find 1.5-4.0\% precision at $r_{\mathrm{Input}} < 24.0$ mag and 
    ${\sim}8$\% precision at $r_{\mathrm{Input}}{\sim}25.2$. 
    For $z$-band we find 1.0-5.0\% precision at $z_{\mathrm{Input}} < 24.0$ mag and 
    ${\sim}10$\% precision down to $z_{\mathrm{Input}}{\sim}25.2$ mag).

@@

	However, Figure \ref{fig:psf_mag} also shows that blending has a strong impact on 
	photometry.  
	On average, \hscpipe{} systematically underestimates the total fluxes of stars 
	that are subject to blending effects by $0.05$--$0.10$ mag at a fixed input 
	magnitude.
    We see the same effect in all bands, and the impact of blendedness becomes
    increasingly significant at fainter magnitudes.
    It is important to bear this caveat in mind when using PSF photometry for point
    sources in HSC data.

	Finally, we also perform similar tests for the \unforced{} PSF photometry in all 
	five bands, and find similar results. 
	To measure the \forced{} PSF photometry, \hscpipe{} fixes the centroid of the PSF 
	model across all five bands. 
	A difference between \forced{} and \unforced{} PSF magnitudes would therefore be 
	an indication of photometric uncertainties arising from inaccurate astrometric 
	calibrations and PSF modeling across different bands\footnote{On average, the 
	centroids are more accurate in \forced{} photometry as they are defined using 
	the band with higher \s2n{}}. 
	Figure \ref{fig:psf_diff} shows the difference between \forced{} and \unforced{} 
	PSF photometry for the $g$ and the $y$ band. 
	The overall differences are small ($<0.01$ mag). 
	At very faint end ($g_{\mathrm{Input}}>24.0$ mag and $g_{\mathrm{Input}}>23.5$

@@

    In Fig \ref{fig:psf_color}, we evaluate the precision and accuracy of the 
    \forced{} $(g-i)$ and $(i-y)$ PSF colors by comparing the differences between input 
    and output colors ($\Delta \mathrm{Color}$) with both the input magnitudes and 
    colors. 
    Figure \ref{fig:psf_color} shows that \hscpipe{} provides precise and accurate PSF 
    colors for synthetic stars with realistic color distributions down to very 
    faint magnitudes. 
    The average precision for $(g-i)$ is ${\sim}0.025$ mag at 
    $i_{\mathrm{Input}}{\sim}19.0$. 
    The scatter increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}24.0$ mag.  
    The $(i-y)$ color displays similar precision. 
    The \forced{} PSF color measurements are not biased through the entire ranges of 
    input magnitudes and colors.

    Figure \ref{fig:psf_color} shows that the precision of PSF colors do not depend 
    the seeing conditions. 
    For instance, the precision of $(g-i)$ for the \texttt{badSeeing} \tract{} is 
    only slightly worse at the very faint end (${\sim}0.14$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the \texttt{goodSeeing} \tract{}.

    Figure \ref{fig:psf_cdist} displays the precision of PSF colors by comparing the 
    color distributions of the input sample to the recovered color distributions. 
    Using four different colors and two color--color planes, we show that the 
    \forced{} PSF colors accurately recover the distributions of all four colors 
    and the color-color distributions.

@@

    Figure \ref{fig:cmodel_sn} shows the relation between the input magnitudes and the 
    \s2n{} of synthetic galaxies.  
    The \s2n{} is the ratio  of the \cmodel{} flux and the flux error measured by 
    \hscpipe{}.
    Here the adopted \s2n{} corresponds to the average \s2n{} over entire footprint. 
    The center of the galaxy typically has high \s2n{} than this value.

    Figure \ref{fig:cmodel_sn} shows that the \cmodel{} photometry displays a 
    well-behaved relation between input magnitude and output \s2n{}.  
    Compared to stars, the \s2n{} from \cmodel{} for synthetic galaxies shows a larger
    scatter at fixed input magnitude. 
    This is likely due to the fact that galaxies have a wider range in sizes and shapes 
    than point sources.  
    In $i$ band, a typical $25.2$ mag galaxy has \s2n{}${\sim}20$ from \cmodel{}, but 
    there are also galaxies at the same magnitude which have \s2n{} below 5. 
    The HSC Wide layer can detect galaxies as faint as $i{\sim}26.0$ mag but the 
    sample becomes incomplete at these faint magnitudes.
    This also introduces a selection bias if galaxies with certain structural 
    properties (e.g., more extended and lower surface brightness) are harder to detect
    than others.
    HSC survey data users who want to select flux-limited galaxy samples,
    or who intend to study the population of faint (e.g., high-$z$) galaxies should
    keep this in mind.  
    Finally, we also find that a worse seeing leads to a lower \s2n{} at fixed 
    magnitude (see Fig \ref{fig:psf_s2n} for $i$-band).

@@

    The overall performance of \cmodel{} photometry is reasonable down to 
    $i_{\mathrm{Input}}=25.2$ mag.
    Compared to the PSF photometry for stars, the statistical uncertainties of \cmodel{} 
    magnitudes are larger for galaxies, which is expected given the diversity of galaxy 
    shapes and sizes that adds complexity to the model-fitting process.
    At the same time, Figure \ref{fig:cmodel_mag} shows that the \cmodel{} algorithm in
    \hscpipe{} provides unbiased and consistent photometry for galaxies across 
    different bands and seeing conditions.

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Astrometric Calibration
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_astrometry}
    \end{center}
    \caption{
        Astrometric accuracy for synthetic stars (\textbf{left}) and galaxies
        (\textbf{right}). We show the differences between the input R.A and Dec and the coordinates measured on the \coadd{} images. Hexagonal bins (filled histogram) and contours (solid-line histogram) are for synthetic objects from \tracts{} with good and bad seeing conditions, 
        respectively.
        $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines. \alexie{Need one phrase here. Always give the take home message in the caption. We find that xxxxxx .}
        }
    \label{fig:astrometry}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Star-Galaxy Separation
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_galaxy}
    \end{center}
    \caption{Evaluation of the \hscpipe{} star--galaxy separation scheme. Star--galaxy separation is based on the the magnitude difference between the PSF and \cmodel{} photometry. The plot on the \textbf{left} (a) corresponds to synthetic stars. Hexagonal bins and filled histogram show distributions of correctly classified
        synthetic stars in the good-seeing \tract{}.
 The scatter plot (dashed-line histogram) and contour (solid-line histogram)
        show distributions of synthetic stars that are misclassified as extended
        objects in \tracts{} with bad and good seeing conditions, respectively.
        The plot on the \textbf{right} (b) corresponds to synthetic 
        galaxies.
        Hexagonal bins (filled histogram) and contours (solid-line histogram)
        are for galaxies from good- and bad-seeing \tracts{}, respectively.
        The scatter plot and dashed-line histogram highlight synthetic galaxies that are
        misclassified as point sources.}
    \label{fig:sg}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Relations between Blendedness and Photomertic Errors
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_blendedness_err}
    \end{center}
    \caption{
        Relation between the $\log(\mathrm{Blendedness})$ parameter
        and the photometric accuracy f synthetic stars (\textbf{upper row}, a and 
        b) and galaxies (\textbf{lower row}, c and d).
        \textbf{Left} columns (a and c) show the uncertainties in PSF and/or \cmodel{} 
        magnitudes. \textbf{Right} columns (b and d) show the uncertainties in 
        $(g-i)$ colors.
        Hexagonal bins and contours show results for good- and bad-seeing
        \tracts{}, respectively.
        $\log(\mathrm{Blendedness}) = -1.0$ is marked using a vertical dashed line.
        }
    \label{fig:blend}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

\section{Other Performace Tests}
    \label{sec:others}

@@

    %to demonstrate the range of topics \synpipe{}
    %can test.

@@

    We inject synthetic objects into single-\visit{} images using the initial (and less accurate) astrometric calibration.
    During the image stacking step, the joint calibration process improves the
    astrometric solutions.
    Therefore, differences between the input and output coordinates from \synpipe{}
    can help us understand systematic effects related to the image stacking step. \alexie{Not clear what we are testing here exactly? Is this an absolute astrometric calibratio for HSC....? Or is this showing how much change there is in the refined astrometric solution??}

    Fig \ref{fig:astrometry} shows the distribution of astrometric offsets for synthetic stars and galaxies in good- and bad-seeing \tracts{}.
    We find small systematic offsets at the ${\sim}10$--20 mas level.
    The two \tracts{} show different systematic offsets.
    In the same \tracts{}, synthetic stars and galaxies show similar offsets, but the scatter for galaxies is slightly larger than stars due to their extended nature. \alexie{Need a final take home message here. What have we learned?}

@@

    Fig \ref{fig:sg} shows the current status of our star--galaxy classification scheme.  Figure  \ref{fig:sg} shows the difference between PSF and \cmodel{}
    magnitudes as a function of  input magnitude. We find that $20$\% of synthetic stars at $i_{\mathrm{Input}}>23.0$ mag are misclassified as extended objects, while only a tiny fraction of faint synthetic galaxies ($i_{\mathrm{Input}}>24.0$) are
    misclassified as stars. This confirms that the current star--galaxy classification strategy in \hscpipe{}
    results in a galaxy sample with \textbf{high completeness} and at star sample
    with \textbf{high purity}.

    It is also clear that seeing condition strongly modifies the distributions
    of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$. Worse seeing conditions make star-galaxy separation more challenging. The completeness and purity of galaxy and star samples at the faint end will depend on seeing conditions.

    In the next data release, \hscpipe{} will include an improved star--galaxy classifier which will be based on a machine learning method that takes both shape \alexie{size?} and color 
    information into account.

@@

 Fig \ref{fig:blend} shows the $b$ parameter versus uncertainties in magnitudes and colors. For both PSF and \cmodel{} magnitude distributions, we can see clear trends that 
    total fluxes are systematically underestimated for highly blended ($b>0.05$ for 
    stars or $0.1$ for galaxies) objects.
    This effect is particularly strong for stars.
    As for colors, higher values of $b$ results in higher uncertainties for both
    stars and galaxies, but the trends are different for each.
    Highly blended stars have clearly overestimated \alexie{redder? bluer? what does overestimated mean} $(g-i)$ colors. Highly blended galaxies seem to have  $(g-i)$ colors that are bluer than the 
    true values.

    Blendedness-related uncertainties are not included in the photometric errors 
    released by \hscpipe{}.
    We therefore caution HSC users to treat the highly blended object with
    greater caution.

@@

    In SDSS,  structural parameters like size and shape from \cmodel{} are often
    used to study the evolution galaxies.
    Although the \cmodel{} in \hscpipe{} follows a very similar algorithm, its primary
    goal now is to provide accurate and consistent magnitude and color in all five
    HSC filters for a vast majority of faint, small galaxies.
    To improve the stability of \cmodel{} for these low-\s2n{} and barely resolved
    galaxies, \hscpipe{} uses Bayesian priors on galaxy sizes and axis ratios. However, the current implementation of these priors has a flaw \alexie{Is this just that the prior is wrong? Can we just say that the prior is wrong?} that leads to a severe  underesaimte in the sizes and axis ratios of galaxies.

    Figure \ref{fig:galaxy_ba} demonstrates this issue and compares the  input and measured values of the  \cmodel{} axis ratio. Here, $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ is a \alexie{the weighted sum? The eighted mean?} combination of the
    axis ratios estimated by the exponential and de Vaucouleurs models weighted by 
    their flux ratio.

    Using our \synpipe{} tests, we discovered that one issue is related to the  \cmodel{} \texttt{usePixelWeight} configuration. This option which decides whether to
    use a per-pixel variances as weights in the nonlinear fit. By default, \hscpipe{} chooses \texttt{usePixelWeight}$=$\texttt{False}.
    As one can see, this leads to a significantly overestimated axis ratio for almost
    all galaxies with $i_{\mathrm{Input}}>21.5$ mag\footnote{It also leads to an
    underestimated half-light radius for these galaxies.}.
    At the same time, we also repeat the \synpipe{} run for galaxies with
    \texttt{usePixelWeight}$=$\texttt{True}, and this change clearly mitigates
    the problem. When we use \texttt{usePixelWeight}$=$\texttt{True},
    $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ provides an unbiased axis ratio 
    estimation for galaxies with $i_{\mathrm{Input}}< 24.0$ mag.  This  is a good example  that  demonstrates how the \synpipe{} framework is a valuable tool  for quality control and that can be used to improve \hscpipe{}.

    For the current HSC data release, we warn users against using the sizes and shapes from \cmodel{} to study the structural properties of galaxies with $i_{\mathrm{Input}}>21.5$.

%    At the same time, \synpipe{} will try to help \hscpipe{} improve the details
%    of the \cmodel{} so that it can provide more useful structural information 
%    without hurting its photometric performance.

@@

    %% Short summary
    In February 2017, the HSC survey made its first public data release, and the survey 
    continues to produce increasingly larger amounts of high-quality imaging data.
    To help achieve the designed goals of the survey and to facilitate scientific investigations, we have developed \synpipe{}, a flexible framework based on
    \hscpipe{} and that can be used to perform quality control on the 
    HSC pipeline outputs. \synpipe{} operates by injecting synthetic stars and galaxies into single-\visit{} images. 
    These data are then processed by \hscpipe{} to generate a \coadd{} images and to perform photometry measurements. With this  approach,  \synpipe{} can be used as an end-to-end and realistic test of the full  data reduction process. In this paper, we  use  two \tracts{} in the HSC Wide layer with
    representative seeing conditions (good and bad \alexie{repeat the numbers here}) to test the general behaviors of HSC
    photometry for both stars and galaxies.

@@

        \item The \forced{} PSF photometry provides excellent \alexie{isn't really a god word. Unbiased? Accurate?} measurements of magnitude and color for isolated stars at $18.0 < i < 25.0$.
            The typical uncertainty of HSC forced PSF photometry for stars ranges
            from 0.01 mag at $i{\sim}18.0$ mag to 0.08 mag at $i{\sim}25.0$
            mag (1\%-7\% accuracy in the $i$-band).
            The \forced{} PSF photometry can accurately recover the color--color
            sequences of stars.

        \item The \forced{} \cmodel{} photometry is reliable for synthetic galaxies
            with realistic distributions of structural parameters and colors at
            $20.0 < i < 25.0$ mag.
            The average accuracy of \forced{} \cmodel{} magnitude ranges from
            ${\sim}7$\% at $i{\sim}20.0$ mag to ${\sim}10$\% at $i{\sim}25.0$.
            The \forced{} \cmodel{} colors for galaxies are accurate and unbiased.
            The accuracy of galaxy colors do not dependence on input magnitude \alexie{What does this mean? They become more inaccurate at fainter magnitue, right? So it does depend on color.} or
            color.

@@

        \item Blending ($b>0.1$) has an impact on the accuracy of both PSF and \cmodel{}
            photometry, especially for stars.
            For highly blended stars, the \forced{} PSF photometry overestimates the magnitudes of stars on average by 0.1–-0.2 mag.
            For galaxies, blending effects typically add an additional 0.05 mag
            uncertainty in both magnitude and color estimates.
    \end{enumerate}

@@

        \item The performance of the current star--galaxy separation algorithm in \hscpipe{}
            is not perfect,  and degrades at fainter magnitudes and with poor seeing
            conditions.
            The fraction of stars that are misclassified as extended objects is still
            quite high ($>20$\% at $i> 22.5$ mag).

        \item The nominal \cmodel{} setting  (\texttt{usePixelWeights=True}) results
            in very biased estimates of the shapes and sizes for galaxies. The axis ratio of a galaxy using \cmodel{} is highly overestimated and the effective radius is typically underestimated.  Galaxy shapes and sizes can be more well measured with the \texttt{usePixelWeights=True} option.
            However, that choice may impact the accuracy of the deblender, which we 
            will test in the future.
    \end{enumerate}

>>>>

%% ------------------------------------------------------------------------------------ %%
\subsection{Limitations and Caveats}
    \label{ssec:caveats}

    %% Caveats
    The limitations of the current \synpipe{} include the following:

        \item  \synpipe{} simply adopts the PSF measured by \hscpipe{} and
            uses it as a model of point source and PSF convolution for a galaxy.
            Hence, it cannot be used to test how the uncertainty of the PSF modeling
            affects the photometry and shape measurements.
            This could be important for regions with exquisite seeing 
            (e.g. FWHM${\sim}0.4$\asec{}) that makes the
            PSF modeling difficult, and for accurate WL measurements 
            (see \citealt{HSCDR1}).

@@

    The \s2n{} for PSF photometry is defined as
    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band. 
    Figure \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} 
    in the $g$- and $i$-bands. 
    This figure shows the expected \s2n{} of stars as a function of magnitude in the 
    Wide layer.
    The slopes and scatters of these relations are very similar to the ones using 
    real stars on these two \tracts{}.

    Fig \ref{fig:star_sn} show that seeing conditions impact the \s2n{} of point
    sources at fixed input magnitude.
    In $i$-band, the bad-seeing (0.7\asec{}) \tract{} shows systematically
    lower \s2n{} than the good-seeing (0.5\asec{}) \tract{}.
    The \s2n{} is similar for the two $g$-band \tracts{} because they share similar 
    seeing conditions.

@@

    Fig \ref{fig:psf_mag} also shows that the precision of the PSF photometry is 
    not filter dependent. 
    The precision of \forced{} PSF magnitudes in $r$ and $z$ is similar to the results
    for $i$-band. 
    For $r$ band we find 1.5-4.0\% precision at $r_{\mathrm{Input}} < 24.0$ mag and 
    ${\sim}8$\% precision at $r_{\mathrm{Input}}{\sim}25.2$. 
    For $z$-band we find 1.0-5.0\% precision at $z_{\mathrm{Input}} < 24.0$ mag and 
    ${\sim}10$\% precision down to $z_{\mathrm{Input}}{\sim}25.2$ mag).

@@

	However, Fig \ref{fig:psf_mag} also shows that blending has a strong impact on 
	photometry.  
	On average, \hscpipe{} systematically underestimates the total fluxes of stars 
	that are subject to blending effects by $0.05$--$0.10$ mag at a fixed input 
	magnitude.
    We see the same effect in all bands, and the impact of blendedness becomes
    increasingly significant at fainter magnitudes.
    It is important to bear this caveat in mind when using PSF photometry for point
    sources in HSC data.

	Finally, we also perform similar tests for the \unforced{} PSF photometry in all 
	five bands, and find similar results. 
	To measure the \forced{} PSF photometry, \hscpipe{} fixes the centroid of the PSF 
	model across all five bands. 
	A difference between \forced{} and \unforced{} PSF magnitudes would therefore be 
	an indication of photometric uncertainties arising from inaccurate astrometric 
	calibrations and PSF modeling across different bands\footnote{On average, the 
	centroids are more accurate in \forced{} photometry as they are defined using 
	the band with higher \s2n{}}. 
	Fig \ref{fig:psf_diff} shows the difference between \forced{} and \unforced{} 
	PSF photometry for the $g$ and the $y$ band. 
	The overall differences are small ($<0.01$ mag). 
	At very faint end ($g_{\mathrm{Input}}>24.0$ mag and $g_{\mathrm{Input}}>23.5$

@@

    In Fig \ref{fig:psf_color}, we evaluate the precision and accuracy of the 
    \forced{} $(g-i)$ and $(i-y)$ PSF colors by comparing the differences between input 
    and output colors ($\Delta \mathrm{Color}$) with both the input magnitudes and 
    colors. 
    Fig \ref{fig:psf_color} shows that \hscpipe{} provides precise and accurate PSF 
    colors for synthetic stars with realistic color distributions down to very 
    faint magnitudes. 
    The average precision for $(g-i)$ is ${\sim}0.025$ mag at 
    $i_{\mathrm{Input}}{\sim}19.0$. 
    The scatter increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}24.0$ mag.  
    The $(i-y)$ color displays similar precision. 
    The \forced{} PSF color measurements are not biased through the entire ranges of 
    input magnitudes and colors.

    Fig \ref{fig:psf_color} shows that the precision of PSF colors do not depend 
    the seeing conditions. 
    For instance, the precision of $(g-i)$ for the \texttt{badSeeing} \tract{} is 
    only slightly worse at the very faint end (${\sim}0.14$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the \texttt{goodSeeing} \tract{}.

    Fig \ref{fig:psf_cdist} displays the precision of PSF colors by comparing the 
    color distributions of the input sample to the recovered color distributions. 
    Using four different colors and two color--color planes, we show that the 
    \forced{} PSF colors accurately recover the distributions of all four colors 
    and the color-color distributions.

@@

    Fig \ref{fig:cmodel_sn} shows the relation between the input magnitudes and the 
    \s2n{} of synthetic galaxies.  
    The \s2n{} is the ratio  of the \cmodel{} flux and the flux error measured by 
    \hscpipe{}.
    Here the adopted \s2n{} corresponds to the average \s2n{} over entire footprint. 
    The center of the galaxy typically has high \s2n{} than this value.

    Fig \ref{fig:cmodel_sn} shows that the \cmodel{} photometry displays a 
    well-behaved relation between input magnitude and output \s2n{}.  
    Compared to stars, the \s2n{} from \cmodel{} for synthetic galaxies shows a larger
    scatter at fixed input magnitude. 
    This is likely due to the fact that galaxies have a wider range in sizes and shapes 
    than point sources.  
    In $i$ band, a typical $25.2$ mag galaxy has \s2n{}${\sim}20$ from \cmodel{}, but 
    there are also galaxies at the same magnitude which have \s2n{} below 5. 
    The HSC Wide layer can detect galaxies as faint as $i{\sim}26.0$ mag but the 
    sample becomes incomplete at these faint magnitudes.
    This also introduces a selection bias if galaxies with certain structural 
    properties (e.g., more extended and lower surface brightness) are harder to detect
    than others.
    HSC survey data users who want to select flux-limited galaxy samples,
    or who intend to study the population of faint (e.g., high-$z$) galaxies should
    keep this in mind.  
    Finally, we also find that a worse seeing leads to a lower \s2n{} at fixed 
    magnitude (see Fig \ref{fig:psf_s2n} for $i$-band).

@@

    The overall performance of \cmodel{} photometry is reasonable down to 
    $i_{\mathrm{Input}}=25.2$ mag.
    Compared to the PSF photometry for stars, the statistical uncertainties of \cmodel{} 
    magnitudes are larger for galaxies, which is expected given the diversity of galaxy 
    shapes and sizes that adds complexity to the model-fitting process.
    At the same time, Fig \ref{fig:cmodel_mag} shows that the \cmodel{} algorithm in
    \hscpipe{} provides unbiased and consistent photometry for galaxies across 
    different bands and seeing conditions.

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Astrometric Calibration
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_astrometry}
    \end{center}
    \caption{
        Astrometric accuracy for synthetic stars (\textbf{left}) and galaxies
        (\textbf{right}). 
        We show the differences between the input R.A and Dec and the coordinates 
        measured on the \coadd{} images. 
        Hexagonal bins (filled histogram) and contours (solid-line histogram) are 
        for synthetic objects from \tracts{} with good and bad seeing conditions, 
        respectively.
        $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines.     
        \song{We find that xxxxxx}.
        }
    \label{fig:astrometry}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Star-Galaxy Separation
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_galaxy}
    \end{center}
    \caption{Evaluation of the \hscpipe{} star--galaxy separation scheme. 
        Star--galaxy separation is based on the the magnitude difference between the 
        PSF and \cmodel{} photometry. 
        The plot on the \textbf{left} (a) corresponds to synthetic stars. 
        Hexagonal bins and filled histogram show distributions of correctly classified
        synthetic stars in the good-seeing \tract{}.
        The scatter plot (dashed-line histogram) and contour (solid-line histogram)
        show distributions of synthetic stars that are misclassified as extended
        objects in \tracts{} with bad and good seeing conditions, respectively.
        The plot on the \textbf{right} (b) corresponds to synthetic galaxies.
        Hexagonal bins (filled histogram) and contours (solid-line histogram)
        are for galaxies from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{},
        respectively.
        The scatter plot and dashed-line histogram highlight synthetic galaxies that 
        are misclassified as point sources.}
    \label{fig:sg}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Relations between Blendedness and Photomertic Errors
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_blendedness_err}
    \end{center}
    \caption{
        Relation between the $\log_{10} (\mathrm{Blendedness})$ parameter
        and the photometric accuracy f synthetic stars (\textbf{upper row}, a and 
        b) and galaxies (\textbf{lower row}, c and d).
        \textbf{Left} columns (a and c) show the uncertainties in PSF and/or \cmodel{} 
        magnitudes. \textbf{Right} columns (b and d) show the uncertainties in 
        $(g-i)$ colors.
        Hexagonal bins and contours show results for \texttt{goodSeeing} and
        \texttt{badSeeing} \tracts{}, respectively.
        $\log_{10} (\mathrm{Blendedness}) = -1.0$ is marked using a vertical dashed 
        line.
        }
    \label{fig:blend}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

\section{Other Performance Tests}
    \label{sec:others}

@@

@@

    We inject synthetic objects into single-\visit{} images using the initial (and 
    less accurate) astrometric calibration.
    During the image stacking step, the joint calibration process improves the
    astrometric solutions.
    Therefore, differences between the input and output coordinates from \synpipe{}
    can help us understand how much has the joint calibration step changes the 
    astrometric calibration.

    Fig \ref{fig:astrometry} shows the distribution of astrometric offsets for 
    synthetic stars and galaxies in \texttt{goodSeeing} and \texttt{badSeeing} 
    \tracts{}.
    We find small systematic offsets at the ${\sim}10$--20 mas level.
    The two \tracts{} show different systematic offsets.
    In the same \tracts{}, synthetic stars and galaxies show similar offsets, but 
    the scatter for galaxies is slightly larger than stars due to their extended 
    nature.

@@

    Fig \ref{fig:sg} shows the current status of our star--galaxy classification 
    scheme.  
    Fig \ref{fig:sg} shows the difference between PSF and \cmodel{} magnitudes as a 
    function of input magnitude. 
    We find that $20$\% of synthetic stars at $i_{\mathrm{Input}}>23.0$ mag are 
    misclassified as extended objects, while only a tiny fraction of faint synthetic 
    galaxies ($i_{\mathrm{Input}}>24.0$) are misclassified as stars. 
    This confirms that the current star--galaxy classification strategy in \hscpipe{}
    results in a galaxy sample with \textbf{high completeness} and a star sample
    with \textbf{high purity}.

    It is also clear that the seeing condition strongly modifies the distributions
    of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$. 
    Worse seeing condition makes star-galaxy separation more challenging. 
    The completeness and purity of galaxy and star samples at the faint end will 
    depend on seeing conditions.

    In the next data release, \hscpipe{} will include an improved star--galaxy 
    classifier which will be based on a machine learning method that takes both 
    size and color information into account.

@@

    Fig \ref{fig:blend} shows the $b$ parameter versus the difference between input and
    output values for both magnitudes and colors. 
    For both PSF and \cmodel{} magnitude distributions, we can see clear trends that 
    total fluxes are systematically underestimated for highly blended ($b>0.05$ for 
    stars or $0.1$ for galaxies) objects.
    This effect is particularly strong for stars.

    As for colors, higher values of $b$ results in higher statistical uncertainties 
    for both stars and galaxies, but the trends are different for each.
    Highly blended stars have clearly redder $(g-i)$ colors than the input values. 
    Highly blended galaxies seem to have $(g-i)$ colors that are bluer than the 
    true values.

    Blendedness-related uncertainties are not included in the photometric errors 
    released by \hscpipe{}.
    We therefore remind the HSC users to treat the highly blended object with
    greater caution.

@@

    In SDSS, structural parameters like size and shape from \cmodel{} are often used to 
    study the evolution galaxies.
    Although the \cmodel{} in \hscpipe{} follows a similar algorithm, its primary
    goal now is to provide accurate and consistent magnitude and color in all five
    bands for a vast majority of faint, small galaxies.
    To improve the stability of \cmodel{} for these low-\s2n{} and barely resolved
    galaxies, \hscpipe{} uses Bayesian priors on galaxy sizes and axis ratios. 
    However, the current implementation of these priors has a serious bug and leads 
    to severe underestimated sizes and ellipticities of galaxies.

    Fig \ref{fig:galaxy_ba} demonstrates this issue and compares the input and 
    measured values of the \cmodel{} axis ratio. 
    Here, $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ is the flux-weighted sum of the
    axis ratios estimated by exponential and de Vaucouleurs models.

    Using our \synpipe{} tests, we discovered that the bug related to the priors only 
    presents when \texttt{usePixelWeight} configuration is set to \texttt{False} during 
    the data reduction. 
    The parameter controls whether or not the per-pixel variance information is used 
    during the model fitting process.  
    As one can see, this leads to significantly overestimated axis ratios for almost
    all galaxies\footnote{It also leads to underestimated half-light radius for the same
    galaxies.}.
    We repeat the \synpipe{} run for galaxies with 
    \texttt{usePixelWeight}$=$\texttt{True}, and this change clearly mitigates
    the problem. 
    When we use \texttt{usePixelWeight}$=$\texttt{True},
    $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ provides an unbiased axis ratio 
    estimation for galaxies with $i_{\mathrm{Input}}< 24.0$ mag.
    This change is still related to the bug in priors.  
    The actual effect of using per-pixel variance should be very small.  
    The next version of \hscpipe{} will fix this bug, and \synpipe{} will help evaluate 
    the precisions of shape and size measurements. 
    This is a good example that demonstrates how the \synpipe{} framework is valuable  
    for quality control and that can be used to improve \hscpipe{}.

    For the current HSC data release, we warn users against using the sizes and shapes 
    from \cmodel{} to study the structural properties of galaxies.

@@

    %% Short summary
    In February 2017, the HSC survey made its first public data release, and the survey 
    continues to produce increasingly larger amounts of high-quality imaging data.
    To help achieve the designed goals of the survey and to facilitate scientific 
    investigations, we have developed \synpipe{}, a flexible framework based on
    \hscpipe{} and that can be used to perform quality control on the HSC pipeline 
    outputs. 
    \synpipe{} operates by injecting synthetic stars and galaxies into single-\visit{}
    images. 
    These data are then processed by \hscpipe{} to generate \coadd{} images and to 
    perform photometric measurements. 
    With this approach, \synpipe{} can be used as an end-to-end and realistic test of 
    the full data reduction process. 
    In this paper, we use two \tracts{} in the HSC Wide layer with representative 
    seeing conditions (\texttt{goodSeeing} with FWHM$=0.45$\asec{} seeing; 
    \texttt{badSeeing} with FWHM$=0.70$\asec{} seeing) to test the general behaviors 
    of HSC photometry for both stars and galaxies.

@@

        \item The \forced{} PSF photometry provides precise and accurate 
            measurements of magnitude and color for isolated stars at 
            $18.0 < i < 25.0$.
            The typical statistical uncertainties of HSC forced PSF photometry for 
            stars ranges from 0.01 mag at $i{\sim}18.0$ mag to 0.08 mag at 
            $i{\sim}25.0$ mag (1\%-7\% precision in the $i$-band).
            The \forced{} PSF photometry can accurately recover the color--color
            sequences of stars.

        \item The \forced{} \cmodel{} photometry is reliable for synthetic galaxies
            with realistic distributions of structural parameters and colors at
            $20.0 < i < 25.0$ mag.
            The statistical uncertainties of \forced{} \cmodel{} magnitude ranges 
            from ${\sim}7$\% at $i{\sim}20.0$ mag to ${\sim}10$\% at $i{\sim}25.0$.
            The \forced{} \cmodel{} colors for galaxies are precise and are 
            consistent across in all five bands.
            They also do not show biases with input magnitudes and colors.

@@

        \item Blending ($b>0.05$) has an impact on the accuracy of both PSF and 
            \cmodel{} photometry, especially for stars.
            For highly blended stars, the \forced{} PSF photometry overestimates 
            the magnitudes of stars on average by 0.1–-0.2 mag.
            For galaxies, blending effects typically add an additional 0.05 mag
            statistical uncertainty in both magnitude and color estimates.

@@

        \item The performance of the current star--galaxy separation algorithm in 
            \hscpipe{} is not perfect, and degrades at fainter magnitudes and with 
            poor seeing conditions.
            The fraction of stars that are misclassified as extended objects is still
            quite high. 
            $>20$\% of the synthetic stars at $i> 22.5$ mag are misclassified
            \footnote{Note that this does not mean high fraction of contamination 
            in the galaxy sample. Please see Bosch\etal (in prep.) for more 
            details.}

        \item The bug in priors on structural parameters and the 
            \texttt{usePixelWeights=False} nominal setting in \cmodel{} result in         
            in very biased estimates of the shapes and sizes for galaxies. 
            The axis ratio from \cmodel{} is highly overestimated and the effective 
            radius is typically underestimated.  
            This issue hence can also affect the accuracy of star--galaxy 
            classification.
